\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{School of random department names} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge Efficient modeling of timeouts in PRISM \\ \horrule{2pt} \\[0.5cm]

### 2018-06-26 Report/tool_paper.tex
modifying repport
tool_paper change and corrected

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LaTeX Example: Project Report
%
% Source: http://www.howtotex.com
%
% Feel free to distribute this example, but please keep the referral
% to howtotex.com
% Date: March 2011 
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% How to use writeLaTeX: 
%
% You edit the source code here on the left, and the preview on the
% right shows you the result within a few seconds.
%
% Bookmark this page and share the URL with your co-authors. They can
% edit at the same time!
%
% You can upload figures, bibliographies, custom classes and
% styles using the files menu.
%
% If you're new to LaTeX, the wikibook is a great place to start:
% http://en.wikibooks.org/wiki/LaTeX
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Edit the title below to update the display in My Documents
%\title{Project Report}
%
%%% Preamble
\documentclass[paper=a4, fontsize=11pt]{scrartcl}
\usepackage[T1]{fontenc}
\usepackage{fourier}
\usepackage{hyperref}

@@

@@

	%% main text
	\section{Introduction}
	\label{S:1}

@@

	\section{Experimental evaluation}
	\label{S:2}

@@

	\pagebreak
	\subsection{Obtaining precise results for reference}
	\label{S:2.1}

@@

	 In order to compare the precision of the results obtained by the experiments, a trustworthy high-precision reference is needed. To achieve this, we used our own PRISM ACTMC implementation, which is capable of analyzing the given model directly without phase-type fitting. Using our implementation, we have computed the steady-state probabilities for very precise termination epsilon $\epsilon = 10^{-20}$ and compared it to the steady-state probabilities obtained by PRISM CTMC with phase-type fitting for $\epsilon = 10^{-16}$ and $k = 800000$. As shown in Figure \ref{fig:diff_storm_dynamic}, the differences between the computations are smaller than $10^6$. Under the hypothesis that the true result is closer to the result obtained from PRISM ACTMC than to the result obtained from Storm, we can conclude that the PRISM ACTMC can serve as reference with precision at least $10^{-6}$.

	 	\begin{figure}[H]
		\begin{center}
			\includegraphics[trim=0.2cm 0cm 0cm 1.35cm,width=15cm, clip]{picture/New_model/1E-10/diff_storm_dynamic.png}
		\end{center}
		\caption{Absolute difference of steady-state probabilities of the CTMC with phase-type fitting ($\epsilon = 10^{-16}$, $k = 800000$) from PRISM ACTMC ($\epsilon = 10^{-20}$).}
		\label{fig:diff_storm_dynamic}
	\end{figure}

	\pagebreak
	\subsection{Default absolute termination epsilon $\epsilon = 10^{-6}$}
	\label{S:2.2}

@@

	\pagebreak
	\subsection{Lowering absolute termination epsilon to $\epsilon = 10^{-10}$}
	\label{S:2.2}

	For much lower $\epsilon = 10^{-10}$, the precision of the result improves. However, for higher $k$ the precision continues to deteriorate like in Section \ref{S:2.2}. The results are shown in Figure \ref{fig:distance_constant_1E-10_constant_kappa}.

@@

	\pagebreak
	\subsection{Adjusting epsilon $\epsilon = 10^{-10}$ to $k$}
	\label{S:2.3}

@@

	\subsection{Required computation time to obtain precise results}
	\label{S:2.4}

@@

	\pagebreak
	\section{Conclusion}
	We have presented a reliable method for high-precision analysis of PRISM CTMC models with phase-type distributions, that is, adjusting the termination epsilon by the number of phases. However, the large number of phases drastically increases the computation time.

@@

	%% The Appendices part is started with the command \appendix;
	%% appendix sections are then done as normal sections
	%% \appendix

	%% \section{}
	%% \label{}

	%% References
	%%
	%% Following citation commands can be used in the body text:
	%% Usage of \cite is as follows:
	%%   \cite{key}          ==>>  [#]
	%%   \cite[chap. 2]{key} ==>>  [#, chap. 2]
	%%   \citet{key}         ==>>  Author [#]

@@

	\bibliographystyle{model1-num-names}
	\bibliography{sample.bib}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LaTeX Example: Project Report
%
% Source: http://www.howtotex.com
%
% Feel free to distribute this example, but please keep the referral
% to howtotex.com
% Date: March 2011 
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% How to use writeLaTeX: 
%
% You edit the source code here on the left, and the preview on the
% right shows you the result within a few seconds.
%
% Bookmark this page and share the URL with your co-authors. They can
% edit at the same time!
%
% You can upload figures, bibliographies, custom classes and
% styles using the files menu.
%
% If you're new to LaTeX, the wikibook is a great place to start:
% http://en.wikibooks.org/wiki/LaTeX
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Edit the title below to update the display in My Documents
%\title{Project Report}
%
%%% Preamble
\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
%\documentclass[paper=a4, fontsize=11pt]{scrartcl}
%\usepackage[T1]{fontenc}
\usepackage{fourier}
\usepackage{hyperref}

@@

\usepackage[
backend=biber,
style=alphabetic,
citestyle=numeric,
sorting=none,
%sortcae=false                  
%citestyle=authoryear
]{biblatex}

\addbibresource{tool_paper.bib} %Imports bibliography file

@@

	%% main text
	\section{Introduction}
	\label{intro}

@@

	\section{Experimental evaluation}
	\label{experimetal_evaluation}

@@

	%\pagebreak
	\subsection{Obtaining precise results for reference}
	\label{reference}

@@

%%	 In order to compare the precision of the results obtained by the experiments, a trustworthy high-precision reference is needed. To achieve this, we used our own PRISM ACTMC implementation, which is capable of analyzing the given model directly without phase-type fitting. Using our implementation, we have computed the steady-state probabilities for very precise termination epsilon $\epsilon = 10^{-20}$ and compared it to the steady-state probabilities obtained by PRISM CTMC with phase-type fitting for $\epsilon = 10^{-16}$ and $k = 1000000$. As shown in Figure \ref{fig:diff_storm_dynamic}, the differences between the computations are smaller than $10^6$. Under the hypothesis that the true result is closer to the result obtained from PRISM ACTMC than to the result obtained from Storm, we can conclude that the PRISM ACTMC can serve as reference with precision at least $10^{-6}$.%%

	 In order to compare the precision of the results obtained by the experiments, a trustworthy high-precision reference is needed. To achieve this, we have modeled the given D/M/1/10 queue in Oris \cite{Bucci2010}. The steady-state distribution obtained by Oris equals the steady-state distribution obtained by our PRISM ACTMC implementation up to at least 14 digits. Hence, our tool can be considered a trustworthy reference with precision of $10^{-14}$.

	%\pagebreak
	\subsection{Default absolute termination epsilon $\epsilon = 10^{-6}$}
	\label{default_absolute}

@@

	\pagebreak
	\subsection{Lowering absolute termination epsilon to $\epsilon = 10^{-10}$}
	\label{lowering}

	For much lower $\epsilon = 10^{-10}$, the precision of the result improves. However, for higher $k$ the precision continues to deteriorate like in Section \ref{lowering}. The results are shown in Figure \ref{fig:distance_constant_1E-10_constant_kappa}.

@@

	%\pagebreak
	\subsection{Adjusting epsilon $\epsilon = 10^{-10}$ to $k$}
	\label{adjusting}

@@

	\subsection{Required computation time to obtain precise results}
	\label{computation_time}

@@

	%\pagebreak
	\section{Conclusion}
	We have presented a reliable method for high-precision analysis of PRISM CTMC models with phase-type distributions, that is, adjusting the termination epsilon by the number of phases. However, the large number of phases drastically increases the computation time.

@@

	%% The Appendices part is started with the command \appendix;
	%% appendix sections are then done as normal sections
\appendix

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%REFERENCES%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%%
	%% Following citation commands can be used in the body text:
	%% Usage of \cite is as follows:
	%%   \cite{key}          ==>>  [#]
	%%   \cite[chap. 2]{key} ==>>  [#, chap. 2]
	%%   \citet{key}         ==>>  Author [#]

@@

	%\bibliographystyle{model1-num-names}
	%\bibliographystyle{alpha}	
	%\bibliography{tool_paper}
\printbibliography
